A pipeline to analyse time-course gene expression data

### 2020-07-22 scripts/manuscript.Rmd
MAINT rescale_values also seems to work locally

# Now use the results of the previous call to aheatmap to reorder the genes.
# FIXME this line doesn't work
# aheatmap(
#    rescale_values(moanin_model[genes_to_plot,ord])[res$rowInd,],
#    Colv=NA,
#    Rowv=NA,
#    annCol=orderedMeta[, c("Group", "Timepoint")],
#    annLegend=TRUE,
#    annColors=ann_colors,
#    main=paste("Cluster", cluster_to_plot, "(rescaled)"),
#    treeheight=0)

>>>>

# Now use the results of the previous call to aheatmap to reorder the genes.
aheatmap(
    rescale_values(moanin_model[genes_to_plot,ord])[res$rowInd,],
    Colv=NA,
    Rowv=NA,
    annCol=orderedMeta[, c("Group", "Timepoint")],
    annLegend=TRUE,
    annColors=ann_colors,
    main=paste("Cluster", cluster_to_plot, "(rescaled)"),
    treeheight=0)
